Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-12 paper/paper.tex
pass on 4.3

\tname{} uses a composition of heurisitc functions to sort the rules
it produces. Each function uses a different criterion to estimate how
similar a rule, created in the previous step, is to rules from a
public database~\cite{emerging-threats-open} including a total of
\numrulessuri\ rules. We describe in the following each of these
heuristic functions. Each function $f_i$ ranges in the 0-1
domain. \tname{} uses the weighted average of these functions to sort
rules: $\sum{f_i}/|f_i|$.

\subsubsection{Size of a rule}
One element that \tname{} uses to measure similarity of synthesized to
human-created rules is the size of the synthetic rule. Informally,
rules with popular sizes score high whereas inpopular rules score low.

Figure~\ref{fig:distribution-rule-size} shows the histogram of rule
sizes for our rule dataset. The x-axis shows the number of options
included in a rule (up to 10) while the y-axis shows the number of
rules with the corresponding number of options. Note that there are 11
rules with no options. These rules only use the header to signal a
traffic as malicious. Also note that most rules have 2 to 6
options. \tname{} values rules in that size range higher compared to
other sizes.

@@

\noindent
, where $\mathit{len(r)}$ denotes the number of options of a rule $r$,
$\mathit{rules\_per\_size}$ encodes distribution of sizes as a
dictionary mapping sizes to number of associated rules, and
$\mathit{max(rules\_per\_size)}$ returns the maximum number of rules
for any dictionary entry. Consequently, the contribution of size is
proportional to its popularity. For example, the contribution of this
heuristic for a rule with 3 options would be 0.684 (=3,662/5,353)
whereas the contribution of a rule with 9 options would be 14.25
(=763/5,353). Note that the measurement is normalized in the 0-1
range.

\subsubsection{Number of content options.} We empirically observed that content options are very
common. As consequence, we defined a heuristic function that takes the
number of content options into account. We calculate the contribution
of number of content options with the following formula:

@@

\[\frac{\mathit{rules\_per\_number\_of\_contents[len(rule)]}}{\mathit{max(rules\_per\_number\_of\_contents)}}\]

@@

>>>>

\tname{} uses a composition of heurisitc functions to sort the rules
it produces. Each function uses a different criterion to estimate how
similar a rule, created in the previous step, is to rules from a
public database~\cite{emerging-threats-open} including a total of
\numrulessuri\ rules \Luc{acima na seção 4.1 falamos que o dataset contem 27.8K regras. No histograma da fig 7 de fato mostra apenas 25K, mas isso porque decidi colocar nele apenas 11 barras}. We describe in the following each of these
heuristic functions. Each function $f_i$ ranges in the 0-1
domain. \tname{} uses the weighted average \Luc{atualmente eh uma média simples e não ponderada ja q as funções tem o mesmo peso. conversamos na ultima reuniao sobre testar diferentes pesos para cada função, mas n sei quão prioritário eh isso comparado as outras atividades que definimos.} of these functions to sort
rules: $\sum{f_i}/|f_i|$.

\subsubsection{Size of a rule}
One element that \tname{} uses to measure similarity of synthesized to
human-created rules is the size of the synthetic rule. Informally,
rules with popular sizes score high whereas inpopular rules score low.
\Luc{talvez explicitar que "size of a rule" quer dizer a quantidade de opções que ha nela?}
Figure~\ref{fig:distribution-rule-size} shows the histogram of rule
sizes for our rule dataset. The x-axis shows the number of options
included in a rule (up to 10) while the y-axis shows the number of
rules with the corresponding number of options. Note that there are 11
rules with no options. These rules only use the header to signal a
traffic as malicious. Also note that most rules have 2 to 6
options. \tname{} values rules in that size range higher compared to
other sizes.

@@

\noindent
, where $\mathit{len(r)}$ denotes the number of options of a rule $r$,
$\mathit{rules\_per\_size}$ encodes distribution of sizes as a
dictionary mapping sizes to number of associated rules, and
$\mathit{max(rules\_per\_size)}$ returns the maximum number of rules
for any dictionary entry. Consequently, the contribution of size is
proportional to its popularity. For example, the contribution of this
heuristic for a rule with 3 options would be 0.684 (=3,662/5,353)
whereas the contribution of a rule with 9 options would be 0.028
(=154/5,353). Note that the measurement is normalized in the 0-1
range.

\subsubsection{Number of content options.} We empirically observed that content options are very
common. \Luc{Se for preciso temos numeros para fundamentar isso melhor, sao cerca de 70K contents nas 28K regras do dataset} As consequence, we defined a heuristic function that takes the
number of content options into account. We calculate the contribution
of number of content options with the following formula:

@@

\[\frac{\mathit{rules\_per\_number\_of\_contents[len(r)]}}{\mathit{max(rules\_per\_number\_of\_contents)}}\]

@@

\Luc{tudo ok ate aqui}
